Test data

### 2022-07-17 Shiny/Test/Test data.Rmd
Commenting.

### CEO compensation
```{r}
compensation_p <- kreft_html |> 
  group_by(year) |> 
  mutate(
    leder_total = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE)
  ) |> 
  ggplot(aes(year, leder_total, fill = leder_total)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
ggplotly(compensation_p)

compensation_p2 <- kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
ggplotly(compensation_p2)
```

>>>>

### CEO compensation and currency testing
```{r}
compensation_p <- kreft_html |> 
  group_by(year) |> 
  mutate(
    leder_total = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE)
  ) |> 
  ggplot(aes(year, leder_total, fill = leder_total)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
ggplotly(compensation_p)

compensation_p2 <- kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
ggplotly(compensation_p2)

# if else structure to check for uniform currency code?
length(unique(kreft_html$valutakode)) == 1

# Testing with uniform currency
if (length(unique(kreft_html$valutakode)) == 1) {
  kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
}

# Creating data frame with multiple currencies
currency_test <- kreft_html |> 
  mutate(
    valutakode = ifelse(year == 2019, "USD", valutakode)
  )

# Testing new data frame
if (length(unique(currency_test$valutakode)) == 1) {
  currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    currency_test |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = "Note: not all values are denominated in the same currency")
}
```
